Supplemental Materials for the paper: \\Pesticides pollution of small streams in Germany

### 2016-09-15 supplement/Supplemental_Materials.tex

\title{Supplemental Materials for the paper: \\Pesticides pollution of small streams in
Germany}
\author{Eduard Szöcs, Marvin Brinke, Bilgin Karaoglan, Ralf B. Schäfer}

\begin{document}
\maketitle

@@

\chapter{Data Cleaning}
More then 30 datasets have been cleaned and homogenized separately, before combing into a common database.
Cleaning steps comprised (Figure~\ref{fig:data_cleaning} gives a graphical overview).

@@

\chapter{Catchment size - stream width relationships}
We studied the relationship between catchment size based on three datasets containing this informations:
Data delivered by the federal state Thuringia, \citet{vos_organic_2015} and \citet{fernandez_effects_2015} (both from Rhineland-Palatinate).
We fitted to each dataset separately and to the combined dataset a power-function.
The resulting models are shown in Figure \ref{fig:size_width}.

@@

\chapter{Overview on compiled data}
% Overview samples
% table generated in do_overview.R
\input{phchoverview}

@@

\chapter{Effect of precipitation and season on RQ}
\begin{figure}[h]
	\centering
	\includegraphics[width = 0.6\textwidth]{precip}
	\caption{Distribution of precipitation at sampling occasions. top: at sampling date. bottom: at day before sampling.}
	\label{fig:precip}
\end{figure}

@@

\chapter{Pollution of small streams}
\begin{figure}[h]
	\centering
	\includegraphics[width = 0.7\textwidth]{ezgagrirac}
	\caption{Raw data used for the model in equation xxx and Figure xxx of the main article. Color codes the number of RAC exceedances (on a log-scale). Grey points denote sites without any exceedance.}
	\label{fig:ezgagrirac}
\end{figure}
\todo{update refs}

>>>>

%% -------------------------------------------------------------------------
\title{Supplemental Materials for the paper: \\Pesticides pollution of small streams in
Germany}
\author{Eduard Szöcs, Marvin Brinke, Bilgin Karaoglan, Ralf B. Schäfer}

%% -------------------------------------------------------------------------
\begin{document}
\maketitle

@@

%% -------------------------------------------------------------------------
\chapter{Data Cleaning}
More then 30 datasets have been cleaned and homogenized separately, before combing into a common database.
Cleaning steps comprised (Figure~\ref{fig:data_cleaning} gives a graphical overview).

@@

%% -------------------------------------------------------------------------
\chapter{Catchment size - stream width relationships}
We studied the relationship between catchment size based on three datasets containing this informations:
Data delivered by the federal state Thuringia, \citet{vos_organic_2015} and \citet{fernandez_effects_2015} (both from Rhineland-Palatinate).
We fitted to each dataset separately and to the combined dataset a power-function.
The resulting models are shown in Figure \ref{fig:size_width}.

@@

%% -------------------------------------------------------------------------
\chapter{Overview on compiled data}
% Overview samples
% table generated in do_overview.R
\input{phchoverview}

@@

%% -------------------------------------------------------------------------
\chapter{Thresholds for agricultural land use and catchment size}
\begin{figure}[h]
	\centering
	\includegraphics[width = 0.8\textwidth]{ezgagrirac}
	\caption{Raw data used for the model in equation 2 and Figure 3 of the main article. Color codes the number of RAC exceedances (on a log-scale). Grey points denote sites without any exceedance.}
	\label{fig:ezgagrirac}
\end{figure}

%% -------------------------------------------------------------------------
\chapter{Effect of precipitation and season on RQ}
\begin{figure}[h]
	\centering
	\includegraphics[width = 0.8\textwidth]{precip}
	\caption{Distribution of precipitation at sampling occasions. top: at sampling date. bottom: at day before sampling.}
	\label{fig:precip}
\end{figure}

@@

%% -------------------------------------------------------------------------
\chapter{Pesticides in small water bodies}

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.8\textwidth]{pmix}
	\caption{Distribution the number of quantified compounds in the samples from small water bodies.}
	\label{fig:pmix}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width = 0.8\textwidth]{pdetects}
	\caption{Proportion of samples with detects in SWB. Only Compounds with more than 100 samples and 15\% of detects are show.}
	\label{fig:pdetects}
\end{figure}
